---
title: "Quarto Example Document"
author:
  - name: "Aaron Gullickson"
    orcid: 0000-0001-7237-8131
    email: aarong@uoregon.edu
    url: https://aarongullickson.netlify.app/
  - name: Bob Somebody
    orcid: 0000-0001-7233-8131
format: 
  html:
    toc: true
    self-contained: true
  pdf:
    keep-md: false
    keep-tex: true
  docx:
    toc: false
editor: source
execute: 
  warning: false
  error: false
#  echo: false
bibliography: references.bib
csl: american-sociological-review.csl # you can also provide a link here
---

```{r}
#| label: load-stuff
#| echo: false
#| output: false

load("stat_data/popularity.RData")
library(tidyverse)
library(gt)
```

# Top level header

## Second level header

### Third level header

#### Fourth level header

## Quarto

Quarto enables **you** to weave together content and executable code into a finished document. To *learn* more about Quarto see <https://quarto.org>. Here is an example of a parenthetical citation [@mcdaniel2011; @andrew2014].

As @abascal2015 said, you can go to the [Zotero Style Library](https://www.zotero.org/styles) to get a CSL file to style your citations and references.[^1]

[^1]: They did not actually say this.

Here is a new paragraph. <!-- TODO: this is a comment -->

-   Point 1
-   Another point
    -   Subpoint 1
    -   Good idea!

1.  First thing
2.  Second thing
    1.  Subthing

> The only thing we have to fear is fear itself - and hamsters!

## Running Code

When you click the **Render** button a [document](https://www.google.com) will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
#| label: calculate-mean

# this is a comment
mean(popularity$nominations)
```

```{r}
#| label: fig-scatter
#| fig-cap: Scatterplot of the relationship between GPA and student popularity.
#| echo: false

ggplot(popularity, aes(x = pseudo_gpa, y = nominations))+
  geom_jitter(alpha = 0.3, width = 0.2)+
  geom_smooth(se = FALSE)+
  labs(x="self-reported GPA in three core courses",
       y="number of friend nominations")+
  theme_bw()
```

This is a text. As @fig-scatter shows, I am right.

```{r}
#| label: tbl-summary
#| tbl-cap: Summary of student statistics by grade

popularity |>
  group_by(grade) |>
  summarize(n = n(), 
            mean_noms = mean(nominations),
            prop_smoke = mean(smoker == "Smoker")) |>
  gt() |>
  cols_label(grade="Grade",
             n="Sample size",
             mean_noms="Mean friend nominations",
             prop_smoke="Percent who smoke") |>
  fmt_number(mean_noms, decimals=2) |>
  fmt_percent(prop_smoke, decimals = 1) |>
  fmt_number(grade, pattern = "{x}th", decimals = 0)
  
  #knitr::kable()
```

As @tbl-summary, shows, this is cool.

You can add options to executable code like this.

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).

# References
