---
title: "Quarto Example Document"
author:
  - name: "Aaron Gullickson"
    orcid: 0000-0001-7237-8131
    email: aarong@uoregon.edu
    url: https://aarongullickson.netlify.app/
  - name: Bob Somebody
    orcid: 0000-0001-7233-8131
format: 
  html:
    toc: true
  pdf:
    keep-md: false
    keep-tex: false
editor: visual
---

# Top level header

## Second level header

### Third level header

#### Fourth level header

## Quarto

Quarto enables **you** to weave together content and executable code into a finished document. To *learn* more about Quarto see <https://quarto.org>.

- Point 1
- Another point
    - Subpoint 1
    - Good idea!

1. First thing
3. Second thing
    1. Subthing
    
> The only thing we have to fear is fear itself - and hamsters!

## Running Code

When you click the **Render** button a [document](https://www.google.com) will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
x <- 2
x^2
```

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
